### 2018-09-13 manuscript.tex
Working on MS

\newcommand{\comment}[1]{\textbf{[[#1]]}}

@@

@@

It was estimated that more than 200 million women, of which 44 millions were girls under age 15, have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16} (to update), and the actual numbers might in fact higher \cite{GaluKama15} (more?).  The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see http://www.who.int/mediacentre/factsheets/fs241/en/ for update).  FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).

The commonly shared position for FGC is more about eradication than intervention \cite{Toub94, Mack96, UNIC16} (more cites); but the progress is hindered due to the complicated history of the very practice.  The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to religious identity in one end and to human rights on the other \cite{Boyl02, SchuLien13, WHO12} (more cites).  Interventions based on associating FGC with violations of human rights and health dangers also encountered challenges \cite{MuthSvan15}, for example, for overlooking a discrepant tolerance between FGC and male circumcision \cite{DarbSvob07, JohnEsse10}, the complexity of woman's autonomy \cite{Meye00}, and cultural perspectives of local history and identity, therefore was often defied by local communities, despite that the practice was often endorsed by national governments \cite{Boyl02, BoylMcMo02, BoylCarb10, Grue05, Koom14, PerrSeni13, Shel08, ShelWand13, Wade11} (update cites).

There are at least three main theoretical perspectives from outside the communities
shedding lights on the complexities of FGC \cite{Hayf05, Youn02}:  social convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.)  Basically, the conventional theory posits FGC an important tool to control marriage fidelity and social prestige; this perspective views FGC as social behaviour resulting of group practice, and it takes a "critical mass" to initiate a change \cite{Mack00, MackLeJe09}.  When norms within the communities are strong, individuals tend to self-enforce the norms of what the community expect from their behaviours \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social network which is intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.
+ \cite{Shel-Wand11}:  Mackie's social convetional theory was supported in their findings; futher, they proposed that fgc practice is beyond the belief of marriage advanges; it goes beyond.  FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriges was not men's refusal of non-fgc women, but hostality and discrimination from fgc women to non fgc women.

The modernization theory proposes that traditional social relationships and values would be impacted by the development of modernization and replaced with modern life styles (e.g., with the improvement of wealth and education and emphasis of individual rights) (see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?).  There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman’s empowerment on making FGC decision are shared concerns:  for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}.  Although conventional theory was well studied and showed a larger effect on FGC practices than other theories of modernization and feminism (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), the aforementioned theories did not necessarily excluded each other, especially between modern theory and feminist theory \cite{Hayf05}.

Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.  Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}, and a community-based FGC perspective \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11, KandNwak09, OdukAfol17} (to confirm) should also be recognized.  This study takes both the dynamics of attitudes and intention of FGC practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test the three theories aforementioned.

\subsection{Research Questions}\label{research-questions}
The main focus of this study is to analyze associations of attitudes of FGC benefits (see the list of FGC benefits at table xx) and intention (planned behavior) to cut daughters.  Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits, FGC continuance and intention (planned behavior) of cutting daughters (structural models) (to explain why)

\_\_{[}CF: read \cite{Aske05, Brue05}{]}

@@

There were two primary sources of FGC data: the Demographic and Health Surveys (DHS) by USAID and the Multiple Indicator Cluster Survey (MICS) directed by UNICEF \cite{CappMone13, YodeWang13}. We used DHS data for this study because of certain questionnaires only available in DHS.  Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We did not analyze the newest dataset due to the lack of FGC benefits modules before this study finished for publication (checked in 09/17).

Only women with daughters to be considered for fgc were included in the main model (the daughter model) and the future-dughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.

@@

The main constrcuts analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} and applied in fgc studies (e.g., \{IloDarf18, PashPonn16}(more cites?). The theory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.  Here, we refer the attitudes to women's attitudes of FGC benefits (see the list of FGC benefits at table-- in Appendix); perceived behavioral control to perception of gender awareness (i.e., women's attitudes towards domestic violence (see the list of attitudes towards domestic violence against women at table xx) and to their social resources (education, and job?) (feminism and modernization?); and the perceived social pressures (subjective norms) as the community level of attitudes of FGC benefits and FGC prevalence (to reflect the convention norms of FGC under the convention theory). \cf{need comments!!!}

@@

\_\_{[}CF: Cluster, which is usually larger than a village but small enough to be a social community, was used to represent a community level of impact \cite{Hayf05} (is Hayf05 correct or DHS method changes afterwards?{]}
\_\_{[}JD: Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess. CF: Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.  But as J said, it is too hard! {]} %“explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior. “ \cite{Hayf05}
\_\_{[}CF:Spatial Bayesian model \cite{KandNwak09} "Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level. Consequently, the spatial analysis will be affected by some random fluctuations.  Some of this random variation can be reduced through structured spatial effects because it includes neighboring observations in the analysis. However, it should be pointed out that such a spatial analysis should preferably be applied to census data, where the precision of the spatial analysis would be much higher." (p. 788){]}

@@

\_\_{[}CF:  Our response ARE categorical not binary; AND still need to explain why ethinicity is a random effect. AND media use was supposed to be incorporated as a random factor at the country level, based on the assumption that media content likely varied among countries.{]}

\_\_{[}CF: reference: Methods and the first paragraph of Discussion\cite{Chia14}{]}

@@

\_\_{[}CF: findings on convention theory vs. modernization theory vs. gender theory{]}

@@

--Main interpretation --
--- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs. modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} (more and confirm).  
% women's empowerment appeared to be more important in explaining differences across communities\cite{ModrLiu13} (more).
% "attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
--- community levels of impact and intervention
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm), 
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}
--- attitudes vs. norm (beliefs) vs. intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intentio:  attitude, norm and perceived behavioroal control.
\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on "coordination."  The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.  But it is likely that fgc is much less an action for marraige proposal but a social indentity to the group they indentify with.
\cite (The social construction of reality: a treatise in the sociology of knowledge Anchor Books, New York, NY (1966))

@@

--- by nations
---- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
1. comparison: \cite{Chia14, Hayf05}, and [http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya]
---- Mali: "The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali. The populations of these countries share certain social and historical ties, which suggests that a strategy to eliminate FGM/C in one of these countries might be successful in others. FGM/C is practiced as part of the initiation into a secret society in Liberia and Sierra Leone. We should expect that the repercussions for mothers there who do not send their daughters to be initiated would be different than for mothers in nearby Mali or Guinea \cite{YodaWang13}

---- Nigeria: "Modernization (education and high socioeconomic status) had minimal impact on the likelihood of FGM, but education plays an important role in the mother's decision not to circumcise her daughter. It follows from these findings that community factors have a large effect on FGM, with individual factors having little effect on the distribution of FGM" \cite{KandNwak09}

@@

\comment{cf: how to cite \cite{AkhmWord13,EffeVogt15} and compare these two?}
% There are "discrepancies between attitudes and practices, especially significant under an analysis by sex as, despite manifesting less support, the percentage of female HCPs declaring to have performed medicalization is almost twice the males’ average. These findings suggest that female HCPs could be facing higher demand to medicalize the practice, and that, even when brought to the medical setting, FGM/C is regarded as a women’s issue to be performed by women to women." \cite{KaplSing16}

@@

%Because of the social aspects associated with FGC, including gender norms and power relations, it is fundamentally important that intervention of FGC practice adopts a holistic approach to focus both on individual and the wider social dynamics \cite{BrowBeec13}. 
 \cite{Shel-Wand11}:  supporting Mackie's convetion theory "expections regarding fgc are interdependent...."

@@

% “FGC facilitates the accumulation of social capital by younger women and of power and prestige by elder women. Based on this new evidence and reinterpretation of social convention theory, we suggest that interventions aimed at eliminating FGC should target women's social networks, which are intergenerational, and include both men and women. Our findings support Mackie's assertion that expectations regarding FGC are interdependent; change must therefore be coordinated among interconnected members of social networks." \cite{ShelWand11}

FGC is still in practice or a preference among women after migrated to a western environment from their original communities where FGC was a common practice, in the hope (wording?) of preserving their ethnic and gender identity despite its conflict against the  norms and laws of the newly settled society \cite{}; however, a baseline study in Sweden showed that a majority of female immigrants, including those newly arrived, opposed all forms of FGC with increased opposition over time after migration, and suggested that an attitude change had occurred \cite{WahlJohn17}; that suggested a likely influence of conventional theory.

(There are also studies proposing various factors impacting FGC practices, such as women's education \cite{KandNwak09,VanMeek15}, social economic status \cite{} etc, community levels of influences.) (What is conventional in convention theory can also be focal points to gender awareness and modern development.  Question:  What is the differences between conventional theory and community level of impact on FGC? the same or?)

@@

% Spatial Bayesian model \cite{KandNwak09}
% idea of purity of women reflects on the status and honor of their families \cite{Ortn87}.  Female purity is oriented to an ideal and unattainable higher class. \cite{Ortn87}
% a possibility of a multicultural egalitarian society \cite{Wade11}
% success in community education program to abandon FGC \cite{DiopAske09}
%\cf{convention theory mainly work on norms or also on behaviour change?  There seems a gap between norm and behaviour in FGC, can diffusion theory brigade the gap?  As suggested, community-based education program has fallen shot tin changing FGC behaviours \cite{Shel08}}
% ”I do not deny that individuals have evolved the capability to learn and apply social norms even to situations that are completely new, but there is much evidence that we are conditional followers of norms. In fact, as the experiments reported in Bicchieri and Xiao (2009) and Bicchieri and Chavez (2010) show, manipulating information produces major changes in behavior, and the existence of a social norm is no guarantee that it will be followed. The real challenge we face is to explain how normative expectations emerge or, in other words, how the beliefs that support social norms take shape." \cite{Bicc10}.

\_\_{[}CF: empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}{[}

@@

% From modifying the practice to discarding it through a process of conversations and understanding  \cite{Mutu02, Shel08}
% findings in \cite{BoylMcMo02}
%* "These finding are particularly informative because most modernization analyses only consider attitude change. The most plausible interpretation is that attitudes change before behavior, and that our analysis captured women in the midst of change." (p. 22)
%"The greater probability of favoring FGC in Egypt was statistically significant compared to all other countries;" (p.22) (This finding is against modern theory/development theory).
%"Our findings suggest that regional development influences attitudes and behavior, but national resistance to international norms can outweigh the influence of regional development." (p.23)
%* "We hypothesized that those carriers of the scripts of the international system – education, mass media and working in the paid economy – would affect women’s attitudes and behavior with respect to FGC. These hypotheses were confirmed" (p. 23) "Older women were less likely to favor the continuation of circumcision, although each year of age increased the probability that a woman had or planned to circumcise her daughters by 6 percent. Older women may have cut their daughters before there was international pressure opposing the practice. The reverse effect for attitudes is consistent with prior findings (see Williams and Sobieszczyk, 1997). It may be an artifact of the survey technique. Older women who oppose FGC may feel freer to say so than younger women because older women are accorded considerable independence in Muslim societies (see, for example, Geiger, 1997).20" (p.24)

% "This study suggests that the adoption of a ‘modern’ lifestyle is not an inevitable result of acquiring the tools that give a person mastery over nature. Rather, the transmission of particular ideologies through global institutionalized arrangements appears to be the critical factor in abandoning practices like FGC." \cite{(BoylMcMo02}, p. 26)  What does this mean???

@@

% \cite{BergDeni13}: application/public policy “A realist synthesis of controlled studies to determine the effectiveness of interventions to prevent genital cutting of girls.“

@@

% norm/attitude vs. behaviour:  attitudes towards fgc did not have a positive correlation with their behaviour:  “within each country women from more developed regions, women who worked outside the home, and educated women were less likely to favor genital cutting and less likely to have their daughters cut. Living in an urban area decreased the likelihood of favoring genital cutting, but it had no effect on behavior. “ \cite{BoylMcMo02}

%\cf{Bicchieri’s norm theory—
behaviour:  What the responder do 
personal normative behaviour:  What the responder believes she should do
empirical expectation:  What the responder believes others do
normative expectation: What the responder believes others think she should do
\cite{Bicc06}
First, what is the association of woman's beliefs in FGC benefits (see the list of FGC benefits at table--) \_\_{[}CF:i.e., normative norm?{]}
and their position on continuing FGC in the future (also normative norm?)  It is called FGC future model.  Second, what is the association of woman's beliefs in FGC benefits and their daughters' FGC status %\cf{empirical norm?}?

@@

% “ the effectiveness of interventions was hampered by a general lack of information. However, through the realist synthesis we identified that all of the interventions were based on a theory that dissemination of information improves cognitions about FGM/C, but the interventions’ success was contingent upon a range of contextual factors. “ \cite{BergDeni12a}

>>>>

\newcommand{\comment}[1]{\textbf{[[#1]]}}
\newcommand{\jd}[1]{\comment{JD: #1}}
\newcommand{\cf}[1]{\comment{CF: #1}}

@@

\jd{I don't understand the North-South framing. Isn't MC not challenged everywhere? Shouldn't the framing be gender?}

@@

It was estimated that more than 200 million women, of which 44 millions were girls under age 15, \jd{This ratio seems super-low. I would expect a majority under 15, no?} have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16} (to update), and the actual numbers might in fact higher \cite{GaluKama15} (more?).  The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see http://www.who.int/mediacentre/factsheets/fs241/en/ for update) \jd{This claim is surprising, and the sources are not academic.}.  FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it \jd{What: implies a degree of self-awareness and} is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).

The commonly shared position for FGC is more about eradication than intervention \cite{Toub94, Mack96, UNIC16} (more cites); but the progress is hindered due to the complicated history of the very practice.  The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to religious identity in one end and to human rights on the other \cite{Boyl02, SchuLien13, WHO12} (more cites).  Interventions based on associating FGC with violations of human rights and health dangers also encountered challenges \cite{MuthSvan15}, for example, for overlooking a discrepant tolerance between FGC and male circumcision \cite{DarbSvob07, JohnEsse10}, the complexity of woman's autonomy \cite{Meye00}, and cultural perspectives of local history and identity, therefore was often defied by local communities, despite that the practice was often endorsed by national governments \cite{Boyl02, BoylMcMo02, BoylCarb10, Grue05, Koom14, PerrSeni13, Shel08, ShelWand13, Wade11} (update cites). \jd{I think we have two choices. Either we accept the WHO ``consensus'' that it's always bad, or start discussing types.}

\jd{It's convention theory. Don't say ``conventional'' theory, that just means the accepted theory in a time and place.}
There are at least three main theoretical perspectives \jd{WHAT: from outside the communities}
shedding lights on the complexities of FGC \cite{Hayf05, Youn02}:  social convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.)  Convention theory posits FGC an important tool to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.  When norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social networks, which are intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.
+ \cite{Shel-Wand11}:  Mackie's social convention theory was supported in their findings \jd{Whose findings? I've lost track of this s.}; futher, they proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects. FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women \jd{It continues to be unclear who is saying what. And what you're implying about their evidence.}.

Modernization theory proposes that traditional social relationships and values would be eroded by modernization (e.g., with the improvement of wealth and education and emphasis of individual rights) (see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?).  There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns:  for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}.  Although convention theory was well studied and showed a larger effect on FGC practices than other theories of modernization and feminism (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), the aforementioned theories did not necessarily excluded each other, especially between modern theory and feminist theory \cite{Hayf05}.

\jd{Can you figure out how to not use ``smart" quotes? They mess up the latex.}

Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.  Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}, and a community-based FGC perspective \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11, KandNwak09, OdukAfol17} (to confirm) should also be recognized.  This study takes both the dynamics of attitudes and intention of FGC practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test the three theories aforementioned. \jd{This P. seems insufficient to tie the theoretical explanation to our research questions. We should study Efferson's approach.}

\subsection{Research Questions}\label{research-questions}
The main focus of this study is to analyze associations of attitudes of FGC benefits (see the list of FGC benefits at table xx) and intention (planned behavior) to cut daughters.  Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits, FGC continuance and intention (planned behavior) of cutting daughters (structural models) (to explain why) 
\jd{I can work on the structural part, but we need a clear explanation of what we are trying to learn from the main question.}
\jd{I guess this is also a good place to discuss our community variables?}

\cf{read \cite{Aske05, Brue05}}

@@

There are two primary sources of FGC data: the Demographic and Health Surveys (DHS) by USAID and the Multiple Indicator Cluster Survey (MICS) directed by UNICEF \cite{CappMone13, YodeWang13}. We used DHS data for this study because of certain questionnaires \jd{``Certain questions'' sounds weaselly. Also, it's not clear we need to talk about MICS; using DHS seems very reasonable.} only available in DHS.  Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We did not analyze the newest dataset due to the lack of FGC benefits modules before this study finished for publication (checked in 09/17).

Only women \jd{What does this mean: with daughters to be considered} for fgc were included in the main model (the daughter model) and the future-dughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\jd{We need to know how DHS decided who to ask the question.}

@@

\jd{Is this s. about us or not? Why is it in our Methods?} The main constructs analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} and applied in fgc studies (e.g., \{IloDarf18, PashPonn16}(more cites?). The theory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to perform the behavior (or not); and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.  Here, we refer the attitudes to women's attitudes of FGC benefits (see the list of FGC benefits at table XX in Appendix); perceived behavioral control to perception of gender awareness (i.e., women's attitudes towards domestic violence (see the list of attitudes towards domestic violence against women at table xx) and to their social resources (education, and job?) (feminism and modernization?); and the perceived social pressures (subjective norms) as the community level of attitudes of FGC benefits and FGC prevalence (to reflect the convention norms of FGC under the convention theory). \cf{need comments!!!} \jd{Not sure what you're trying to do here. What do you mean by ``refer''? Seems loose.}

@@

\jd{How did the comments get so messed up? Can it not happen again?}
\cf{Cluster, which is usually larger than a village but small enough to be a social community, was used to represent a community level of impact \cite{Hayf05} (is Hayf05 correct or DHS method changes afterwards?}
\jd{Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.} \cf{Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.  But as J said, it is too hard! } %``explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior. `` \cite{Hayf05}
\cf{Bayesian model \cite{KandNwak09} ``Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level. Consequently, the spatial analysis will be affected by some random fluctuations.  Some of this random variation can be reduced through structured spatial effects because it includes neighboring observations in the analysis. However, it should be pointed out that such a spatial analysis should preferably be applied to census data, where the precision of the spatial analysis would be much higher." (p. 788)}

@@

\cf{Our response ARE categorical not binary; AND still need to explain why ethinicity is a random effect. AND media use was supposed to be incorporated as a random factor at the country level, based on the assumption that media content likely varied among countries.}

\cf{reference: Methods and the first paragraph of Discussion\cite{Chia14}}

@@

\cf{findings on convention theory vs. modernization theory vs. gender theory}

@@

--Main interpretation --
--- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs. modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} (more and confirm).  
% women's empowerment appeared to be more important in explaining differences across communities\cite{ModrLiu13} (more).
% ``attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
--- community levels of impact and intervention
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm), 
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}
--- attitudes vs. norm (beliefs) vs. intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intentio:  attitude, norm and perceived behavioroal control.
\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on ``coordination."  The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.  But it is likely that fgc is much less an action for marraige proposal but a social indentity to the group they indentify with.
\cite (The social construction of reality: a treatise in the sociology of knowledge Anchor Books, New York, NY (1966))

@@

--- by nations
---- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
1. comparison: \cite{Chia14, Hayf05}, and [http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya]
---- Mali: ``The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali. The populations of these countries share certain social and historical ties, which suggests that a strategy to eliminate FGM/C in one of these countries might be successful in others. FGM/C is practiced as part of the initiation into a secret society in Liberia and Sierra Leone. We should expect that the repercussions for mothers there who do not send their daughters to be initiated would be different than for mothers in nearby Mali or Guinea \cite{YodaWang13}

---- Nigeria: ``Modernization (education and high socioeconomic status) had minimal impact on the likelihood of FGM, but education plays an important role in the mother's decision not to circumcise her daughter. It follows from these findings that community factors have a large effect on FGM, with individual factors having little effect on the distribution of FGM" \cite{KandNwak09}

@@

\comment{cf: how to cite \cite{AkhmWord13,EffeVogt15} and compare these two?}
% There are "discrepancies between attitudes and practices, especially significant under an analysis by sex as, despite manifesting less support, the percentage of female HCPs declaring to have performed medicalization is almost twice the males' average. These findings suggest that female HCPs could be facing higher demand to medicalize the practice, and that, even when brought to the medical setting, FGM/C is regarded as a women's issue to be performed by women to women." \cite{KaplSing16}

@@

%Because of the social aspects associated with FGC, including gender norms and power relations, it is fundamentally important that intervention of FGC practice adopts a holistic approach to focus both on individual and the wider social dynamics \cite{BrowBeec13}. 
 \cite{Shel-Wand11}:  supporting Mackie's convetion theory ``expections regarding fgc are interdependent...."

@@

% ``FGC facilitates the accumulation of social capital by younger women and of power and prestige by elder women. Based on this new evidence and reinterpretation of social convention theory, we suggest that interventions aimed at eliminating FGC should target women's social networks, which are intergenerational, and include both men and women. Our findings support Mackie's assertion that expectations regarding FGC are interdependent; change must therefore be coordinated among interconnected members of social networks." \cite{ShelWand11}

FGC is still in practice or a preference among women after migrated to a western environment from their original communities where FGC was a common practice, in the hope (wording?) of preserving their ethnic and gender identity despite its conflict against the  norms and laws of the newly settled society \cite{}; however, a baseline study in Sweden showed that a majority of female immigrants, including those newly arrived, opposed all forms of FGC with increased opposition over time after migration, and suggested that an attitude change had occurred \cite{WahlJohn17}; that suggested a likely influence of convention theory.

(There are also studies proposing various factors impacting FGC practices, such as women's education \cite{KandNwak09,VanMeek15}, social economic status \cite{} etc, community levels of influences.) (What is conventional in convention theory can also be focal points to gender awareness and modern development.  Question:  What is the differences between convention theory and community level of impact on FGC? the same or?)

@@

% Spatial Bayesian model \cite{KandNwak09}
% idea of purity of women reflects on the status and honor of their families \cite{Ortn87}.  Female purity is oriented to an ideal and unattainable higher class. \cite{Ortn87}
% a possibility of a multicultural egalitarian society \cite{Wade11}
% success in community education program to abandon FGC \cite{DiopAske09}
%\cf{convention theory mainly work on norms or also on behaviour change?  There seems a gap between norm and behaviour in FGC, can diffusion theory brigade the gap?  As suggested, community-based education program has fallen shot tin changing FGC behaviours \cite{Shel08}}
% "I do not deny that individuals have evolved the capability to learn and apply social norms even to situations that are completely new, but there is much evidence that we are conditional followers of norms. In fact, as the experiments reported in Bicchieri and Xiao (2009) and Bicchieri and Chavez (2010) show, manipulating information produces major changes in behavior, and the existence of a social norm is no guarantee that it will be followed. The real challenge we face is to explain how normative expectations emerge or, in other words, how the beliefs that support social norms take shape." \cite{Bicc10}.

\cf{empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}}

@@

% From modifying the practice to discarding it through a process of conversations and understanding  \cite{Mutu02, Shel08}
% findings in \cite{BoylMcMo02}
%* "These finding are particularly informative because most modernization analyses only consider attitude change. The most plausible interpretation is that attitudes change before behavior, and that our analysis captured women in the midst of change." (p. 22)
%"The greater probability of favoring FGC in Egypt was statistically significant compared to all other countries;" (p.22) (This finding is against modern theory/development theory).
%"Our findings suggest that regional development influences attitudes and behavior, but national resistance to international norms can outweigh the influence of regional development." (p.23)
%* "We hypothesized that those carriers of the scripts of the international system – education, mass media and working in the paid economy – would affect women's attitudes and behavior with respect to FGC. These hypotheses were confirmed" (p. 23) "Older women were less likely to favor the continuation of circumcision, although each year of age increased the probability that a woman had or planned to circumcise her daughters by 6 percent. Older women may have cut their daughters before there was international pressure opposing the practice. The reverse effect for attitudes is consistent with prior findings (see Williams and Sobieszczyk, 1997). It may be an artifact of the survey technique. Older women who oppose FGC may feel freer to say so than younger women because older women are accorded considerable independence in Muslim societies (see, for example, Geiger, 1997).20" (p.24)

% "This study suggests that the adoption of a `modern' lifestyle is not an inevitable result of acquiring the tools that give a person mastery over nature. Rather, the transmission of particular ideologies through global institutionalized arrangements appears to be the critical factor in abandoning practices like FGC." \cite{(BoylMcMo02}, p. 26)  What does this mean???

@@

% \cite{BergDeni13}: application/public policy ``A realist synthesis of controlled studies to determine the effectiveness of interventions to prevent genital cutting of girls.``

@@

% norm/attitude vs. behaviour:  attitudes towards fgc did not have a positive correlation with their behaviour:  ``within each country women from more developed regions, women who worked outside the home, and educated women were less likely to favor genital cutting and less likely to have their daughters cut. Living in an urban area decreased the likelihood of favoring genital cutting, but it had no effect on behavior. `` \cite{BoylMcMo02}

%\cf{Bicchieri's norm theory—
behaviour:  What the responder do 
personal normative behaviour:  What the responder believes she should do
empirical expectation:  What the responder believes others do
normative expectation: What the responder believes others think she should do
\cite{Bicc06}
First, what is the association of woman's beliefs in FGC benefits (see the list of FGC benefits at table--) \cf{normative norm?}
and their position on continuing FGC in the future (also normative norm?)  It is called FGC future model.  Second, what is the association of woman's beliefs in FGC benefits and their daughters' FGC status %\cf{empirical norm?}?

@@

% `` the effectiveness of interventions was hampered by a general lack of information. However, through the realist synthesis we identified that all of the interventions were based on a theory that dissemination of information improves cognitions about FGM/C, but the interventions' success was contingent upon a range of contextual factors. `` \cite{BergDeni12a}
